Supplementary Material: Bayesian multi-proxy reconstruction of early Eocene latitudinal temperature gradients

### 2023-05-24 manuscript/supplementary.qmd
discussion part 2 and proofreading checks

---
title: "Supplementary Material: Bayesian multi-proxy reconstruction of latitudinal temperature gradients applied to the Early Eocene"
author:
  - "---"
  - Kilian Eichenseer^1^ and Lewis A. Jones^2^
  - "---"
  - "^1^Department of Earth Sciences, Durham University, South Road, DH1 3LE, Durham, United Kingdom"
  - "^2^Centro de Investigación Mariña, Grupo de Ecoloxía Animal, Departamento de Ecoloxía e Bioloxía Animal, Universidade de Vigo, 36310 Vigo, Spain."
  - "---"
  - "**Corresponding author:** kilian.eichenseer@durham.ac.uk"
format:
  docx:
    reference-doc: template.docx
    highlight-style: github
    fig-dpi: 900
  pdf:
    documentclass: scrartcl
    papersize: letter
    geometry:
      - top=25.4mm
      - bottom=25.4mm
      - left=25.4mm
      - right=25.4mm
      - heightrounded
crossref:
  fig-title: Supplementary Figure
  fig-prefix: Supplementary Figure
bibliography: references.bib
csl: climate-of-the-past.csl
---

>>>>

---
title: "Supplementary Material: Bayesian multi-proxy reconstruction of early Eocene latitudinal temperature gradients"
author:
  - "---"
  - Kilian Eichenseer^1^ and Lewis A. Jones^2^
  - "---"
  - "^1^Department of Earth Sciences, Durham University, South Road, DH1 3LE, Durham, United Kingdom"
  - "^2^Centro de Investigación Mariña, Grupo de Ecoloxía Animal, Departamento de Ecoloxía e Bioloxía Animal, Universidade de Vigo, 36310 Vigo, Spain."
  - "---"
  - "**Corresponding author:** kilian.eichenseer@durham.ac.uk"
format:
  docx:
    reference-doc: template.docx
    highlight-style: github
    fig-dpi: 900
  pdf:
    documentclass: scrartcl
    papersize: letter
    geometry:
      - top=25.4mm
      - bottom=25.4mm
      - left=25.4mm
      - right=25.4mm
      - heightrounded
crossref:
  fig-title: Supplementary Figure
  fig-prefix: Supplementary Figure
bibliography: references.bib
csl: climate-of-the-past.csl
---
